Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
revise introduction
above cited -> aforementioned
then -> subsequently
well designed -> well-designed

Unfortunately, those fields of research are still in infancy and consequently very few well built datasets are readily available for evaluation purposes for the signal processing community. A closely related field of investigation that is relatively more mature is the classification of acoustic scenes whose aim is to predict labels by processing audio data. Despite being narrower in terms of range of applications, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data processing field for a while, with availability of some well designed evaluation datasets.

Despite the differences, the following question is valid both for the above cited future application and the acoustic scene classification (ASC) task. How can we efficiently and effectively process large amount of audio data using representations that are both compact, generic in their design and with a large potential application range ?

The research described in this paper attempt to provide answers to that question by demonstrating the usefulness of two main contributions: 1) the use of the time scattering transform allows us to extract discriminative features with very few parameter optimization and 2) object-based modeling of the acoustic scene based on unsupervised clustering of each acoustic scene  allows us to effectively focus the description of the scene on areas of interest.

The proposed approach is motivated in Section \ref{sec:motivations}  and a brief review the state of the art in the field of acoustic scene modeling is performed in Section \ref{sec:soa}. Then, the contributions are extensively described in Section \ref{sec:scattering} and \ref{sec:object}, respectively. Experiments carried out in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC) are then reported in Section \ref{sec:experiments}.

>>>>

Unfortunately, the field of signal-based eco-acoustics is still in infancy.
As a consequence, very few well built datasets are readily available for evaluation purposes.
A closely related field of investigation, which is relatively more mature, is the classification of acoustic scenes whose aim is to predict labels by processing audio data.
Despite being narrower in terms of range of applications, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data mining community for a while, with availability of a few well-designed datasets.

Despite the differences, the following question is valid both for the aforementioned future application and the acoustic scene classification (ASC) task: how can we efficiently and effectively process a large amount of audio data using representations that are compact, generic in their design, and with a large range of potential applications ?

The research described in this paper attempt to provide answers to this question by demonstrating the usefulness of two main contributions: 1) the use of the scattering transform allows us to extract discriminative features with few parameter optimization and 2) object-based modeling of the acoustic scene based on unsupervised clustering of each acoustic scene allows to effectively focus the description of the scene on areas of interest.

The proposed approach is motivated in Section \ref{sec:motivations} and a brief review the state of the art in the field of acoustic scene modeling is given in Section \ref{sec:soa}. Then, the contributions are extensively described in Section \ref{sec:scattering} and \ref{sec:object}, respectively. Experiments carried out in an unsupervised setting, \textit{i.e.} acoustic scene similarity (ASS) and in a supervised setting, \textit{i.e.}  acoustic scene classification (ASC) are subsequently reported in Section \ref{sec:experiments}.
